How to build an homogeneous language for heterogeneous platforms

### 2013-06-10 papers/gpce2013/gpce2013.tex
figures

>>>>

\begin{figure}
\centering
\includegraphics[width=8cm]{microbenchmark.png}
\caption{Micro-benchmark on the optional values abstraction}
\label{micro-benchmark}
\end{figure}

Figure \ref{micro-benchmark} shows the micro-benchmark results. We measured the runtime performance, the number of
lines of code (as an indication of the abstraction level), and finally the ratio of runtime performance and lines of
code. \emph{js-scala} is between 3 to 100 times faster than other approaches on our benchmark. Combined with that
fact that it provides high-level abstractions, it has a performance / lines of code ratio more than 4 times higher
than other approaches.
